$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-09-22 paper/paper.tex
Update LOCs
Keep line numbers within column margins

\begin{example}[Variable reference]
  \autoref{lst:channels} types a variable reference under a linear algebra.
  \begin{lstlisting}[label=lst:channels,mathescape,numbers=left,caption=Typing variable reference $\suc \constr{0}$ with type $\channel{\unit}{\li}$ and usage $\li$.]
$\_ \; : \; \contains{\constr{[]} \comma \channel{\unit}{\li} \comma \unit} {\constr{[]} \comma \lio \comma \lio} {\suc \constr{0}} {\channel{\unit}{\li}} {\li} {\constr{[]} \comma \lo \comma \lio}$
$\_ \; = \; \suc \constr{0}$

@@

In this paper we provide a well-scoped syntax and a semantics for the \picalc{}, extrinsically define a type system on top of the syntax capable of handling linear, graded and shared types under the same unified framework and show that reduction preserves the well-typedness of processes.
We avoid the need for extrinsic context splits by defining a type system based on leftover typing \cite{Allais2018a}, which is defined here for the first time for the \picalc{}.
As a result, theorems like framing, weakening and strengthening can now we stated for the linear \picalc{}.
Our work is fully mechanised in around 1500 lines of code in Agda%
\begin{anonsuppress}
\cite{Zalakain2020Agda}
\end{anonsuppress}
.

>>>>

\begin{example}[Variable reference]
  \autoref{lst:channels} types a variable reference under a linear algebra.
  \begin{lstlisting}[label=lst:channels,xleftmargin=15pt,mathescape,numbers=left,caption=Typing variable reference $\suc \constr{0}$ with type $\channel{\unit}{\li}$ and usage $\li$.]
$\_ \; : \; \contains{\constr{[]} \comma \channel{\unit}{\li} \comma \unit} {\constr{[]} \comma \lio \comma \lio} {\suc \constr{0}} {\channel{\unit}{\li}} {\li} {\constr{[]} \comma \lo \comma \lio}$
$\_ \; = \; \suc \constr{0}$

@@

In this paper we provide a well-scoped syntax and a semantics for the \picalc{}, extrinsically define a type system on top of the syntax capable of handling linear, graded and shared types under the same unified framework and show that reduction preserves the well-typedness of processes.
We avoid the need for extrinsic context splits by defining a type system based on leftover typing \cite{Allais2018a}, which is defined here for the first time for the \picalc{}.
As a result, theorems like framing, weakening and strengthening can now we stated for the linear \picalc{}.
Our work is fully mechanised in around 1850 lines of code in Agda%
\begin{anonsuppress}
\cite{Zalakain2020Agda}
\end{anonsuppress}
.
